---
title: "Visualize Data"
output: github_document
author: Joseph Randolph
---

## Your Turn 0

Add a setup chunk that loads the tidyverse packages.

```{r setup, include=False}
knitr:: opts_chunk$set(echo = TRUE)
library(tidyverse)

```

```{r}
data(mpg)
summary(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
ggplot(data=mpg)+
  geom_point(mapping = aes(x = displ, y= hwy))

```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#similar to previous gg plot
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy),binwidth = 2) #no y variamle ad bin windth outside astetics

c <- ggplot(mpg, aes(hwy))#from cheat sheet
c + geom_histogram(binwidth = 5) 



```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#similar to previous gg plot
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy),binwidth = 2) #no y variamle ad bin windth outside astetics
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#ggplot(data = mpg) +
 # geom_point(mapping = aes(x = displ, y = hwy))
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color= class)) # add 'color= class' to get color and key

#use asign ment in code
f <- ggplot(data = mpg)
f+geom_point(mapping = aes(x = displ, y = hwy, color= class))#aes =astetics color, shape, size mus t go in astetics
#f+geom_point(mapping = aes(x = displ, y = hwy, color= class, size=class))#add size dosent look good
#f+geom_point(mapping = aes(x = displ, y = hwy, shape= class))#add shape dosent look good
#f+geom_point(mapping = aes(x = displ, y = hwy, shape= class,size=class,color= class))# add multiple  customizations
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
ggplot(data = mpg) +
  geom_bar(mapping = aes(x = hwy),)
```

## Quiz

What will this code do?

```{r}
ggplot(mpg) + 
  geom_point(aes(displ, hwy)) +
  geom_smooth(aes(displ, hwy))
```


***

# Take aways

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```